Paradigms in Physics 2.0

### 2018-09-28 proposal.tex
Suggestions from Liz

\begin{abstract}
In 2016, the Department of Physics at Oregon State University began a
process to revise our Paradigms in Physics curriculum for physics
majors.  We began with a colloquium to inform the department of our
plans and request their assistance, followed by a
survey of students and faculty as well as individual interviews with
the faculty teaching each course.  As we developed a plan to
address student- and faculty-identified challenges in the curriculum,
we met with each faculty member individually to explain and refine our
proposal, which was unanimously approved by the faculty.  Major
changes include major changes to several courses (math
methods, computational physics, modern physics, electronics, and
classical mechanics), including the introduction of two sophomore-year
courses designed specifically to help prepare students for their
upper-division courses.
\end{abstract}

@@

@@

\paragraph*{Research questions}
\begin{itemize}
\item What was the educational reform context within which the faculty
  initiated revising the upper-level physics curriculum?
\item What was the culture of the department at that time? In
  particular, what were the participants' beliefs about teaching and
  learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the new program?
\item How did the faculty develop and communicate plans for this new
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with an unanimous vote?
\end{itemize}
\paragraph*{Research methods}
We performed interviews of faculty before, during and after the
Paradigms 2.0 process, gave surveys to students and faculty, and had
an observer take notes during all Paradigms 2.0 meetings.

>>>>

@@

In 2016, the Department of Physics at Oregon State University began a
process to revise our Paradigms in Physics curriculum for physics
majors.  We began with a colloquium to inform the department of our
plans and request their assistance, followed by a
survey of students and faculty as well as individual interviews with
the faculty teaching each course.  As we developed a plan to
address student- and faculty-identified challenges in the curriculum,
we met with each faculty member individually to explain and refine our
proposal, which was unanimously approved by the faculty.  Major
changes include major changes to several courses (math
methods, computational physics, modern physics, electronics, and
classical mechanics), including the introduction of two sophomore-year
courses designed specifically to help prepare students for their
upper-division courses.

@@

\paragraph*{Research questions}
\begin{itemize}
\item What was the culture of the department when the faculty initiated revising the upper-level physics curriculum? In
  particular, what were the participants' beliefs about teaching and
  learning?
\item What motivated making changes and how did the faculty form a
  coherent vision for the new program?
\item How did the faculty develop and communicate plans for this new
  curriculum?
\item How have they changed instruction based upon the proposals that
  the faculty approved with an unanimous vote?
\end{itemize}
\paragraph*{Research methods}
We performed interviews of faculty before, during and after the
Paradigms 2.0 process, gave surveys to students and faculty, and had
an observer take notes during all Paradigms 2.0 meetings.
